humanCdGF_predict_cfu

### 2016-10-10 code/HumanCdGF_predict_cfu.Rmd
remove early euth samples

# remove samples not used or with other cdiff strains
meta_file <- 
  meta_file %>% 
  filter(cdiff_strain == 431, !cage_id == 'NP1') %>% 
  select(mouse_id, sample_id, day, log_cfu) %>% 
  filter(!is.na(log_cfu))

@@

### All OTUs input to Random Forest
```{r all otus, fig.width=10, fig.height=6}
ggdraw()+
  draw_plot(heat.plot(rsq, '#003300', legend_title = expression(paste('R'^'2'))), 0, 0, 0.5, 1) + 
  draw_plot(heat.plot(mse, 'white', '#000066', 'MSE'), 0.5, 0, 0.5, 1)
#plot(otu_votes[otu_votes >= 10], xlab = 'OTU', ylab = 'Freq')
```

@@

###### Re-runnning the program and only focusing on the OTUs predicting day 9/10 to see if there is consistence in the predictive features gives the following selection:  
Otu00004 Otu00005 Otu00015 Otu00019 Otu00030 Otu00199 Otu00200 Otu00250   
      14       17       13       15       13       16       17       19

>>>>

# remove samples not used or with other cdiff strains
meta_file <- 
  meta_file %>% 
  filter(Early_Euth == FALSE, cdiff_strain == 431, !cage_id == 'NP1') %>% 
  select(mouse_id, sample_id, day, log_cfu) %>% 
  filter(!is.na(log_cfu))

@@

### All OTUs input to Random Forest - without mice euthanized early
```{r all otus, fig.width=10, fig.height=6}
ggdraw()+
  draw_plot(heat.plot(rsq, '#003300', legend_title = expression(paste('R'^'2'))), 0, 0, 0.5, 1) + 
  draw_plot(heat.plot(mse, 'white', '#000066', 'MSE'), 0.5, 0, 0.5, 1)
#plot(otu_votes[otu_votes >= 10], xlab = 'OTU', ylab = 'Freq')
```

@@

###### Re-runnning the program and only focusing on the OTUs predicting day 9/10 to see if there is consistence in the predictive features gives the following selection  (including all samples):  
Otu00004 Otu00005 Otu00015 Otu00019 Otu00030 Otu00199 Otu00200 Otu00250   
      14       17       13       15       13       16       17       19
